\begin{frame}[allowframebreaks]{References}
    \bibliographystyle{apalike}
    \begin{thebibliography}{99}
        \bibitem{hinton2006reducing}
        Hinton, G. E., \& Salakhutdinov, R. R. (2006).
        Reducing the dimensionality of data with neural networks.
        \textit{Science}, 313(5786), 504-507.

        \bibitem{vincent2008extracting}
        Vincent, P., Larochelle, H., Bengio, Y., \& Manzagol, P. A. (2008).
        Extracting and composing robust features with denoising autoencoders.
        In \textit{Proceedings of the 25th international conference on Machine learning} (pp. 1096-1103).

        \bibitem{kingma2013auto}
        Kingma, D. P., \& Welling, M. (2013).
        Auto-encoding variational Bayes.
        \textit{arXiv preprint arXiv:1312.6114}.

        \bibitem{makhzani2015adversarial}
        Makhzani, A., Shlens, J., Jaitly, N., Goodfellow, I., \& Frey, B. (2015).
        Adversarial autoencoders.
        \textit{arXiv preprint arXiv:1511.05644}.

        \bibitem{bengio2013representation}
        Bengio, Y., Courville, A., \& Vincent, P. (2013).
        Representation learning: A review and new perspectives.
        \textit{IEEE transactions on pattern analysis and machine intelligence}, 35(8), 1798-1828.

        \bibitem{baldi2012autoencoders}
        Baldi, P. (2012).
        Autoencoders, unsupervised learning, and deep architectures.
        In \textit{Proceedings of ICML Workshop on Unsupervised and Transfer Learning} (pp. 37-49).

        \bibitem{goodfellow2016deep}
        Goodfellow, I., Bengio, Y., \& Courville, A. (2016).
        Deep Learning.
        MIT Press.
    \end{thebibliography}
\end{frame}