\section{References}
\begin{frame}{References}
  These slides have been adapted from
  \begin{itemize}
    \item Younes Mourri \& Lukasz Kaiser, \href{https://www.deeplearning.ai/courses/natural-language-processing-specialization/}{Natural Language Processcing Specialization, DeepLearning.AI}
  \end{itemize}
\end{frame}

\begin{frame}{References}
  \textbf{Foundational Papers:}
  \begin{itemize}
    \item Hochreiter, S., \& Schmidhuber, J. (1997). \textit{Long Short-Term Memory}. Neural Computation.
    \item Cho, K., van Merriënboer, B., Gulcehre, C., Bahdanau, D., Bougares, F., Schwenk, H., \& Bengio, Y. (2014). \textit{Learning Phrase Representations using RNN Encoder--Decoder with GRU}. EMNLP.
    \item Pascanu, R., Mikolov, T., \& Bengio, Y. (2013). \textit{On the difficulty of training RNNs}. ICML.
    \item Bengio, Y., Simard, P., \& Frasconi, P. (1994). \textit{Learning long-term dependencies}. IEEE Transactions on Neural Networks.
    \item Vaswani, A., Shazeer, N., Parmar, N., Uszkoreit, J., Jones, L., Gomez, A. N., Kaiser, L., \& Polosukhin, I. (2017). \textit{Attention Is All You Need}. NeurIPS.
  \end{itemize}
\end{frame}

\begin{frame}{References}
  \textbf{Resources:}
  \begin{itemize}
    \item Karpathy's RNN Blog:\\
    \href{https://karpathy.github.io/2015/05/21/rnn-effectiveness/}{\texttt{https://karpathy.github.io/2015/05/21/rnn-effectiveness/}}
    \item CS231n Lecture Notes on RNNs and LSTM
    \item DeepLearning.ai NLP Specialization --- Coursera
    \item MIT 6.S191 Deep Learning Lecture Slides
  \end{itemize}
\end{frame}
