\begin{frame}{References}
  \begin{itemize}
    \item These slides have been adapted from
    \item Bhiksha Raj \& Rita Singh, 11-785 Introduction to Deep Learning, CMU
  \end{itemize}
\end{frame}

\begin{frame}{References}
  \footnotesize
  \begin{enumerate}
    \item Vaswani, A., Shazeer, N., Parmar, N., Uszkoreit, J., Jones, L., Gomez, A. N., Kaiser, L., \& Polosukhin, I. (2017). Attention is All You Need. \textit{In NeurIPS}.
    \item Devlin, J., Chang, M. W., Lee, K., \& Toutanova, K. (2019). BERT: Pre-training of Deep Bidirectional Transformers. \textit{In NAACL}.
    \item Radford, A., Wu, J., Child, R., Luan, D., Amodei, D., \& Sutskever, I. (2019). Language Models are Unsupervised Multitask Learners (GPT-2). OpenAI.
    \item Raffel, C., Shazeer, N., Roberts, A., Lee, K., Narang, S., Matena, M., Zhou, Y., Li, W., \& Liu, P. J. (2020). Exploring the Limits of Transfer Learning with a Unified Text-to-Text Transformer (T5). \textit{JMLR}.
    \item Zhou, H., Zhang, S., Ma, S., \& Sun, J. (2022). RMSNorm: Root Mean Square Layer Normalization. arXiv preprint arXiv:1910.07467.
    \setcounter{enumi}{5}
    \item Dao, T., Fu, T., Ermon, S., Rudra, A., \& Ré, C. (2022). FlashAttention: Fast and Memory-Efficient Exact Attention with IO-Awareness. In \textit{NeurIPS}.
    \item Beltagy, I., Peters, M. E., \& Cohan, A. (2020). Longformer: The Long-Document Transformer. arXiv preprint arXiv:2004.05150.
    \item Tay, Y., Dehghani, M., Bahri, D., \& Metzler, D. (2020). Efficient Transformers: A Survey. arXiv preprint arXiv:2009.06732.
  \end{enumerate}
\end{frame}
