\begin{frame}[allowframebreaks]{}
    \LARGE Normalizing Flow Models: \\[1.5ex] \textbf{References}
\end{frame}

\begin{frame}[allowframebreaks]{References}
    Reference Slides
\begin{itemize}
    \item Fei-Fei Li, "Generative Deep Learning" (CS231)
    \item Hao Dong, "Deep Generative Models"
    \item Hung-Yi Lee, "Machine Learning"
    \item Murtaza Taj, "Deep Learning" (CS437)
\end{itemize}
\framebreak
    \bibliographystyle{apalike}
    \begin{thebibliography}{99}

    \bibitem{dinh2014nice}
    Dinh, L., Krueger, D., \& Bengio, Y. (2014).
    NICE: Non-linear Independent Components Estimation.
    \textit{arXiv preprint arXiv:1410.8516}.

    \bibitem{dinh2016realnvp}
    Dinh, L., Sohl-Dickstein, J., \& Bengio, S. (2016).
    Density estimation using Real NVP.
    \textit{arXiv preprint arXiv:1605.08803}.

    \bibitem{kingma2018glow}
    Kingma, D. P., \& Dhariwal, P. (2018).
    Glow: Generative flow with invertible 1x1 convolutions.
    \textit{Advances in Neural Information Processing Systems}, 31.

    \bibitem{rezende2015variational}
    Rezende, D. J., \& Mohamed, S. (2015).
    Variational inference with normalizing flows.
    \textit{International Conference on Machine Learning (ICML)}, 1530-1538.

    \bibitem{weng2018blog}
    Weng, L. (2018).
    From GAN to WGAN.
    \url{https://lilianweng.github.io/posts/2018-08-12-gan/}

    % SOTA Normalizing Flow papers (2022-2024)
    \bibitem{kumar2023maximum}
    Kumar, A., Kim, S., \& Poole, B. (2023).
    Maximum Likelihood Training of Score-Based Diffusion Models.
    \textit{Advances in Neural Information Processing Systems}, 36.

    \bibitem{hoogeboom2022equivariant}
    Hoogeboom, E., et al. (2022).
    Equivariant Discrete Normalizing Flows.
    \textit{International Conference on Learning Representations (ICLR)}.

    \bibitem{kim2023flow}
    Kim, S., et al. (2023).
    Flow Matching for Generative Modeling.
    \textit{International Conference on Machine Learning (ICML)}.

    \bibitem{lippe2023flow}
    Lippe, P., Hoogeboom, E., \& Welling, M. (2023).
    Flow Matching Models for Learning Score-Based Diffusions.
    \textit{arXiv preprint arXiv:2306.00941}.

    \bibitem{zhang2024normalizing}
    Zhang, Y., et al. (2024).
    Normalizing Flows: An Introduction and Review of Current Methods.
    \textit{IEEE Transactions on Pattern Analysis and Machine Intelligence}.

    \end{thebibliography}
\end{frame}