% --- References (Stable Diffusion lecture) ---
\section{References}
\begin{frame}[allowframebreaks]{References}
\textbf{Tutorials and Surveys}
\begin{itemize}
    \item Binxu Wang: \href{https://binxuw.scholars.harvard.edu/sites/g/files/omnuum11221/files/binxuw/files/stable_diffusion_a_tutorial.pdf}{Stable Diffusion: A Tutorial (Harvard ML from Scratch)} --- U-Net, time embedding, CLIP conditioning.
    \item Kreis, K., Gao, R., \& Vahdat, A.: \href{https://cvpr2022-tutorial-diffusion-models.github.io/}{CVPR 2022 Tutorial: Diffusion Models}
    \item Rogge, L., \& Rasul, K.: \href{https://huggingface.co/blog/annotated-diffusion}{The Annotated Diffusion Model}
    \item Lilian Weng: \href{https://lilianweng.github.io/posts/2021-07-11-diffusion-models/}{What are Diffusion Models?}
    \item Yang Song: \href{https://yang-song.github.io/blog/2021/score/}{Score-Based Generative Modeling: A Brief Overview}
\end{itemize}

\framebreak

\textbf{Foundational Diffusion Models}
\begin{itemize}
    \item Ho, J., Jain, A., \& Abbeel, P. (2020). \href{https://arxiv.org/abs/2006.11239}{Denoising Diffusion Probabilistic Models}
    \item Sohl-Dickstein, J., et al.\ (2015). \href{https://arxiv.org/abs/1503.03585}{Deep Unsupervised Learning using Nonequilibrium Thermodynamics}
    \item Song, Y., \& Ermon, S. (2019). \href{https://arxiv.org/abs/1907.05600}{Generative Modeling by Estimating Gradients of the Data Distribution}
    \item Nichol, A., \& Dhariwal, P. (2021). \href{https://arxiv.org/abs/2102.09672}{Improved Denoising Diffusion Probabilistic Models}
\end{itemize}

\framebreak

\textbf{Stable Diffusion: Core Papers}
\begin{itemize}
    \item Rombach, R., et al.\ (2022). \href{https://arxiv.org/abs/2112.10752}{High-Resolution Image Synthesis with Latent Diffusion Models} --- Stable Diffusion / LDM (VAE + U-Net + conditioning).
    \item Radford, A., et al.\ (2021). \href{https://arxiv.org/abs/2103.00020}{Learning Transferable Visual Models From Natural Language Supervision (CLIP)} --- text encoder and cross-attention conditioning.
\end{itemize}

\framebreak

\textbf{Applications and Model Releases}
\begin{itemize}
    \item Nichol, A., et al.\ (2021). \href{https://arxiv.org/abs/2112.10741}{GLIDE: Towards Photorealistic Image Generation and Editing with Text-Guided Diffusion Models}
    \item Ramesh, A., et al.\ (2022). \href{https://arxiv.org/abs/2204.06125}{Hierarchical Text-Conditional Image Generation with CLIP Latents (DALL·E~2)}
    \item Saharia, C., et al.\ (2022). \href{https://arxiv.org/abs/2205.11487}{Photorealistic Text-to-Image Diffusion Models with Deep Language Understanding (Imagen)}
    \item Blattmann, A., et al.\ (2023). \href{https://arxiv.org/abs/2311.15127}{Stable Video Diffusion: Scaling Latent Video Diffusion Models to Large Datasets}
    \item Lopez, J. (2022). \href{https://stability.ai/news-updates/stable-diffusion-v2-release}{Stable Diffusion 2.0 Release} --- OpenCLIP, upscaler, depth2img, inpainting (Stability AI blog).
    \item Stability AI (2024). \href{https://stability.ai/news-updates/introducing-stable-diffusion-3-5}{Introducing Stable Diffusion 3.5} --- SD~3.5 Large / Large Turbo / Medium (Stability AI blog).
    \item Raisinghani, A. (2026). \href{https://blog.google/innovation-and-ai/technology/ai/nano-banana-2/}{Nano Banana 2: Combining Pro capabilities with lightning-fast speed} (Google DeepMind blog).
\end{itemize}
\end{frame}
