\section{References}
\begin{frame}{}
    \LARGE DDQN \& SARSA: \textbf{References}
\end{frame}

\begin{frame}[allowframebreaks]{References}
\begin{thebibliography}{99}

\bibitem{mnih2015}
Mnih, V., Kavukcuoglu, K., Silver, D., et al. (2015).
\newblock Human-level control through deep reinforcement learning.
\newblock \emph{Nature}.

\bibitem{vanhasselt2016}
Van Hasselt, H., Guez, A., Silver, D. (2016).
\newblock Deep Reinforcement Learning with Double Q-learning.
\newblock \emph{AAAI}.

\bibitem{wang2016}
Wang, Z., Schaul, T., Hessel, M., et al. (2016).
\newblock Dueling Network Architectures for Deep RL.
\newblock \emph{ICML}.

\bibitem{rummery1994}
Rummery, G. A., \& Niranjan, M. (1994).
\newblock On-line Q-learning using connectionist systems.
\newblock Technical Report.

\bibitem{sutton2018}
Sutton, R. S., \& Barto, A. G. (2018).
\newblock Reinforcement Learning: An Introduction.

\bibitem{cs285}
Berkeley CS285 Deep RL Lectures.\\
\url{https://rail.eecs.berkeley.edu/deeprlcourse/}

\bibitem{silver}
David Silver’s RL Series.\\
\url{http://www0.cs.ucl.ac.uk/staff/d.silver/web/Teaching.html}

\bibitem{brunskill}
Emma Brunskill, Stanford CS234: Reinforcement Learning.\\
\url{https://web.stanford.edu/class/cs234/}

\bibitem{cs231n}
Fei-Fei Li, Yunzhu Li \& Ruohan Gao, Stanford CS231n: Deep Learning for Computer Vision.\\
\url{http://cs231n.stanford.edu/}

\bibitem{cme241}
Ashwin Rao, Stanford CME241: Foundations of Reinforcement Learning with Applications in Finance.\\
\url{https://web.stanford.edu/class/cme241/}

\bibitem{uoftcsc413}
Jimmy Ba \& Bo Wang, UofT CSC413/2516: Neural Networks and Deep Learning.\\
\url{https://uoft-csc413.github.io/2022/}

\end{thebibliography}
\end{frame}