\section{References}
\begin{frame}{}
    \LARGE Image Segmentation: \textbf{References}
\end{frame}

\begin{frame}[allowframebreaks]{References \& Further Reading}
    \begin{thebibliography}{9}
        \bibitem{long2015fcn}
        Long, J., Shelhamer, E., \& Darrell, T. (2015). 
        \newblock Fully Convolutional Networks for Semantic Segmentation.
        \newblock In \emph{Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition (CVPR)}.
        \newblock \href{https://arxiv.org/abs/1411.4038}{arxiv.org/abs/1411.4038}

        \bibitem{ronneberger2015unet}
        Ronneberger, O., Fischer, P., \& Brox, T. (2015).
        \newblock U-Net: Convolutional Networks for Biomedical Image Segmentation.
        \newblock In \emph{Medical Image Computing and Computer-Assisted Intervention (MICCAI)}.
        \newblock \href{https://arxiv.org/abs/1505.04597}{arxiv.org/abs/1505.04597}

        \bibitem{he2017maskrcnn}
        He, K., Gkioxari, G., Dollár, P., \& Girshick, R. (2017).
        \newblock Mask R-CNN.
        \newblock In \emph{Proceedings of the IEEE International Conference on Computer Vision (ICCV)}.
        \newblock \href{https://arxiv.org/abs/1703.06870}{arxiv.org/abs/1703.06870}

        \bibitem{kirillov2019panoptic}
        Kirillov, A., He, K., Girshick, R., Rother, C., \& Dollár, P. (2019).
        \newblock Panoptic Segmentation.
        \newblock In \emph{Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition (CVPR)}.
        \newblock \href{https://arxiv.org/abs/1801.00868}{arxiv.org/abs/1801.00868}

        \bibitem{strudel2021segmenter}
        Strudel, R., Garcia, R., Laptev, I., \& Schmid, C. (2021).
        \newblock Segmenter: Transformer for Semantic Segmentation.
        \newblock In \emph{Proceedings of the IEEE International Conference on Computer Vision (ICCV)}.
        \newblock \href{https://arxiv.org/abs/2105.05633}{arxiv.org/abs/2105.05633}

        \bibitem{xie2022segformer}
        Xie, E., Wang, W., Yu, Z., Anandkumar, A., Alvarez, J. M., \& Luo, P. (2022).
        \newblock SegFormer: Simple and Efficient Design for Semantic Segmentation with Transformers.
        \newblock In \emph{Advances in Neural Information Processing Systems (NeurIPS)}.
        \newblock \href{https://arxiv.org/abs/2105.15203}{arxiv.org/abs/2105.15203}
    \end{thebibliography}

    \vspace{1em}
    \textbf{Additional Resources:}
    \begin{itemize}
        \item PapersWithCode: \href{https://paperswithcode.com/task/image-segmentation}{paperswithcode.com/task/image-segmentation}
        \item Stanford CS231n Slides (Segmentation Modules): \href{http://cs231n.stanford.edu/slides/2022/}{cs231n.stanford.edu/slides/2022/}
        \item DeepMind Perceiver IO: \href{https://arxiv.org/abs/2107.14795}{arxiv.org/abs/2107.14795}
        \item Google Mask2Former: \href{https://arxiv.org/abs/2112.01527}{arxiv.org/abs/2112.01527}
    \end{itemize}
\end{frame}