\section{References}
\begin{frame}[allowframebreaks]{References}
\textbf{Tutorials and Surveys}
\begin{itemize}
    \item Kreis, K., Gao, R., \& Vahdat, A.: \href{https://cvpr2022-tutorial-diffusion-models.github.io/}{CVPR 2022 Tutorial: Diffusion Models}
    \item Rogge, L., \& Rasul, K.: \href{https://huggingface.co/blog/annotated-diffusion}{The Annotated Diffusion Model}
    \item Yang Song: \href{https://yang-song.github.io/blog/2021/score/}{Score-Based Generative Modeling: A Brief Overview}
    \item Lilian Weng: \href{https://lilianweng.github.io/posts/2021-07-11-diffusion-models/}{What are Diffusion Models?}
\end{itemize}

\framebreak

\textbf{Foundational Papers}
\begin{itemize}
    \item Ho, J., Jain, A., \& Abbeel, P. (2020). \href{https://arxiv.org/abs/2006.11239}{Denoising Diffusion Probabilistic Models}
    \item Sohl-Dickstein, J., Weiss, E., Maheswaranathan, N., \& Ganguli, S. (2015). \href{https://arxiv.org/abs/1503.03585}{Deep Unsupervised Learning using Nonequilibrium Thermodynamics}
    \item Song, Y., \& Ermon, S. (2019). \href{https://arxiv.org/abs/1907.05600}{Generative Modeling by Estimating Gradients of the Data Distribution}
    \item Nichol, A., \& Dhariwal, P. (2021). \href{https://arxiv.org/abs/2102.09672}{Improved Denoising Diffusion Probabilistic Models}
\end{itemize}

\framebreak

\textbf{Applications and Notable Models}
\begin{itemize}
    \item Ramesh, A., et al. (2022). \href{https://arxiv.org/abs/2204.06125}{Hierarchical Text-Conditional Image Generation with CLIP Latents (DALL·E 2)}
    \item Saharia, C., et al. (2022). \href{https://arxiv.org/abs/2205.11487}{Photorealistic Text-to-Image Diffusion Models with Deep Language Understanding (Imagen)}
    \item Nichol, A., Dhariwal, P., et al. (2021). \href{https://arxiv.org/abs/2112.10752}{GLIDE: Towards Photorealistic Image Generation and Editing with Text-Guided Diffusion Models}
    \item Preechakul, T., et al. (2022). \href{https://arxiv.org/abs/2201.09865}{Diffusion Autoencoders: Toward a Meaningful and Decodable Representation}
    \item Saharia, C., et al. (2022). \href{https://arxiv.org/abs/2104.07636}{Image Super-Resolution via Iterative Refinement}
    \item Poole, B., et al. (2022). \href{https://arxiv.org/abs/2206.02736}{DreamFusion: Text-to-3D using 2D Diffusion}
\end{itemize}

\framebreak

\textbf{GANs and Related Reading}
\begin{itemize}
    \item Goodfellow, I., et al. (2014). \href{https://arxiv.org/abs/1406.2661}{Generative Adversarial Nets}
    \item Creswell, A., et al. (2018). \href{https://arxiv.org/abs/1710.07035}{Generative Adversarial Networks: An Overview}
\end{itemize}
\end{frame}