\begin{frame}{}
    \LARGE Contrastive Learning: \textbf{References}
\end{frame}

\begin{frame}[allowframebreaks]{References}
\begin{thebibliography}{99}

\bibitem{simclr}
Ting Chen, Simon Kornblith, Mohammad Norouzi, Geoffrey Hinton. \emph{A Simple Framework for Contrastive Learning of Visual Representations.} ICML 2020. \href{https://arxiv.org/abs/2002.05709}{arXiv:2002.05709}.

\bibitem{byol}
Jean-Bastien Grill et al. \emph{Bootstrap Your Own Latent — A New Approach to Self‑Supervised Learning.} NeurIPS 2020. \href{https://arxiv.org/abs/2006.07733}{arXiv:2006.07733}.

\bibitem{dino}
Mathilde Caron et al. \emph{Emerging Properties in Self‑Supervised Vision Transformers.} ICCV 2021. \href{https://arxiv.org/abs/2104.14294}{arXiv:2104.14294}.

\bibitem{ibot}
Zheng Zhang et al. \emph{iBOT: Image BERT Pre‑Training with Online Token‑Level Distillation.} ICML 2022. \href{https://arxiv.org/abs/2204.03615}{arXiv:2204.03615}.

\bibitem{khvatova2019}
Kristina Khvatova. \emph{Weakly Supervised Learning: Introduction and Best Practices.} Data Science Milan, 2019.

\bibitem{frontiers2021}
Frontiers in AI. \emph{Taxonomy of Weakly Supervised Learning.} 2021.

\bibitem{cao2012}
Liangliang Cao, Zicheng Liu, and Thomas S. Huang. \emph{Weakly Supervised Activity Classification.} Frontiers, 2012.

\bibitem{snorkel}
Alex Ratner et al. \emph{Snorkel: Rapid Training Data Creation with Weak Supervision.} ICML 2016. \href{https://arxiv.org/abs/1711.10160}{arXiv:1711.10160}.

\bibitem{survey}
\textbf{Survey:} Xinlei Chen, Kaiming He. \emph{Exploring Simple Siamese Representation Learning.} CVPR 2021. \href{https://arxiv.org/abs/2011.10566}{arXiv:2011.10566}.

\bibitem{lecun}
\textbf{Tutorial:} Yann LeCun’s Lectures on Self‑Supervised Learning (YouTube).

\bibitem{simclr-code}
\textbf{Code:} \href{https://github.com/google-research/simclr}{SimCLR (TensorFlow)}

\bibitem{byol-code}
\textbf{Code:} \href{https://github.com/lucidrains/byol-pytorch}{BYOL (PyTorch)}

\bibitem{dino-code}
\textbf{Code:} \href{https://github.com/facebookresearch/dino}{DINO (PyTorch)}

\bibitem{ibot-code}
\textbf{Code:} \href{https://github.com/bytedance/ibot}{iBOT (PyTorch)}

\end{thebibliography}
\end{frame}