\section{References}
\begin{frame}{}
    \LARGE Reinforcement Learning: \textbf{References}
\end{frame}

\begin{frame}[allowframebreaks]{References}
    \begin{thebibliography}{99}
        \bibitem{SuttonBarto2018}
        Sutton, R. S., \& Barto, A. G. (2018).
        \newblock \emph{Reinforcement Learning: An Introduction}.

        \bibitem{Williams1992}
        Williams, R. J. (1992).
        \newblock Simple Statistical Gradient-Following Algorithms for Connectionist Reinforcement Learning.
        \newblock \emph{Machine Learning Journal}.

        \bibitem{Schulman2015}
        Schulman, J., Levine, S., Abbeel, P., Jordan, M., \& Moritz, P. (2015).
        \newblock Trust Region Policy Optimization.
        \newblock In \emph{ICML}.

        \bibitem{Schulman2017}
        Schulman, J., Wolski, F., Dhariwal, P., Radford, A., \& Klimov, O. (2017).
        \newblock Proximal Policy Optimization Algorithms.
        \newblock \emph{arXiv preprint arXiv:1707.06347}.

        \bibitem{Haarnoja2018}
        Haarnoja, T., Zhou, A., Abbeel, P., \& Levine, S. (2018).
        \newblock Soft Actor-Critic: Off-Policy Maximum Entropy Deep Reinforcement Learning with a Stochastic Actor.
        \newblock In \emph{ICML}.

        \bibitem{OpenAISpinningUp}
        OpenAI Spinning Up.
        \newblock \url{https://spinningup.openai.com}

        \bibitem{BerkeleyCS285}
        Berkeley CS285 Deep RL.
        \newblock \url{https://rail.eecs.berkeley.edu/deeprlcourse/}

        \bibitem{StanfordCS224R}
        Chelsea Finn \& Karol Hausman, Stanford CS224R: \href{http://cs224r.stanford.edu/}{Deep Reinforcement Learning}

        \bibitem{StanfordCS231n}
        Fei-Fei Li, Yunzhu Li \& Ruohan Gao, Stanford CS231n: \href{http://cs231n.stanford.edu/}{Deep Learning for Computer Vision}

        \bibitem{UofTCSC413}
        Jimmy Ba \& Bo Wang, UofT CSC413/2516: \href{https://uoft-csc413.github.io/2022/}{Neural Networks and Deep Learning}

        \bibitem{BerkeleyCS285FA21}
        Sergey Levine, Berkeley CS285: \href{https://rail.eecs.berkeley.edu/deeprlcourse-fa21/}{Deep Reinforcement Learning}
    \end{thebibliography}
\end{frame}