\section{Benefits of MoE}
\begin{frame}[allowframebreaks]{}
    \LARGE Benefits of MoE
\end{frame}

\begin{frame}[allowframebreaks]{Benefits of MoE}
    \begin{itemize}
        \item \textbf{Scalability:}
        \begin{itemize}
            \item Can scale to billions of parameters.
            \item Only a small subset of experts is activated for each input.
            \item Allows for larger models without proportional increases in compute.
        \end{itemize}
    \framebreak
        \item \textbf{Efficient Computation:}
        \begin{itemize}
            \item Activates only 10–20\% of total parameters per token.
            \item Reduces computational cost per token.
            \item Sparse activation means fewer parameters are active at any time.
            \item Enables training on larger datasets with limited resources.
            \item Leads to lower latency and inference cost.
            \item Allows for models with vastly more parameters.
        \end{itemize}
    \framebreak
        \item \textbf{Flexibility:}
        \begin{itemize}
            \item Different experts can specialize in different tasks or data distributions.
            \item Allows for more nuanced model behavior and adaptability.
            \item Can be tailored to specific applications or domains.
        \end{itemize}
    \framebreak
        \item \textbf{Specialization:}
        \begin{itemize}
            \item Experts can focus on specific domains (e.g., math, code, biology, logic).
            \item Improves accuracy and performance in specialized tasks.
        \end{itemize}
        \item \textbf{Example 1: MoE with Domain Experts}
        \begin{itemize}
            \item A math expert becomes active only on arithmetic inputs.
            \item Improves accuracy specifically for math problems.
            \item Outperforms generalist models on these tasks.
        \end{itemize}
        \item \textbf{Example 2: MORE (Mixture of Reasoning Experts)}
        \begin{itemize}
            \item Explicitly uses experts for types of reasoning (e.g., multihop, factual, analogical).
            \item Boosts performance and provides greater interpretability.
            \item Allows understanding which expert handles which reasoning step.
        \end{itemize}
    \framebreak
        \item \textbf{Performance:}
        \begin{itemize}
            \item Often achieves state-of-the-art results on various benchmarks.
            \item Combines the strengths of multiple models without the overhead of training them separately.
            \item Can outperform dense models with fewer active parameters.
        \end{itemize}
    \end{itemize}
\end{frame}