\section{Limitations of LRMs and MoE Models}
\begin{frame}[allowframebreaks]{}
    \LARGE Limitations of LRMs and MoE Models
\end{frame}

\begin{frame}[allowframebreaks]{Limitations of LRMs and MoE Models}
    \begin{itemize}
        \item \textbf{For LRMs (Large Language Models):}
        \begin{itemize}
            \item \textbf{Verbose outputs:} CoT (Chain-of-Thought) and ToT (Tree-of-Thought) methods generate long outputs.
            \item May confuse end-users due to extensive reasoning traces.
            \item \textbf{Prompt sensitivity:} Small changes in prompt wording lead to large changes in output.
            \item Requires careful prompt engineering.
            \item \textbf{Computation overhead:} Especially with self-consistency sampling or ToT trees.
            \item Increases inference cost and time.
            \item \textbf{Example:} CoT prompting works well on GSM8K (a math dataset), but fails without careful prompt tuning.
            \item Shows sensitivity to specific prompt design.
        \end{itemize}
        \item \textbf{For MoEs (Mixture of Experts):}
        \begin{itemize}
            \item \textbf{Training instability:} Some experts may be underused, leading to "expert collapse."
            \item This is often addressed with load balancing.
            \item \textbf{Hard to debug:} Expert specialization may not always align with human-interpretable domains.
            \item Makes understanding model behavior challenging.
            \item \textbf{Distributed training cost:} Load balancing across GPUs adds significant engineering overhead.
            \item Requires complex distributed systems.
        \framebreak
            \item \textbf{Example 1: GShard training instability}
            \begin{itemize}
                \item Some experts never activate after several epochs of training.
                \item Requires manual intervention or advanced balancing techniques.
            \end{itemize}
            \item \textbf{Example 2: Switch Transformer}
            \begin{itemize}
                \item Needed custom gradient balancing.
                \item To prevent expert overload or dropout during training.
            \end{itemize}
        \end{itemize}
    \end{itemize}
\end{frame}