\section{References \& Further Reading}
\begin{frame}[allowframebreaks]{}
    \LARGE References \& Further Reading
\end{frame}

\begin{frame}[allowframebreaks]{References \& Further Reading}
\begin{itemize}

\item Wei, J., Wang, X., Schuurmans, D., Bosma, M., Ichter, B., Xia, F., Chi, E. H., Le, Q. V., \& Zhou, D. (2022). \emph{Chain-of-Thought Prompting Elicits Reasoning in Large Language Models}. \href{https://arxiv.org/abs/2201.11903}{arXiv:2201.11903}.

\item Wang, X., Wei, J., Schuurmans, D., Le, Q., Chi, E., Narang, S., Chowdhery, A., \& Zhou, D. (2022). \emph{Self-Consistency Improves Chain of Thought Reasoning in Language Models}. \href{https://arxiv.org/abs/2203.11171}{arXiv:2203.11171}.

\item DeepSeek-AI et al. (2025). \emph{DeepSeek-R1: Incentivizing Reasoning Capability in LLMs via Reinforcement Learning}. \href{https://arxiv.org/abs/2501.12948}{arXiv:2501.12948}.

\item Financial Times. (2025). \emph{Transcript: The story behind DeepSeek's breakthrough}. \href{https://www.ft.com/content/d23a01d8-4256-4142-a52c-a393ed6df1bc}{ft.com}.

\item Shazeer, N., Mirhoseini, A., Maziarz, K., Davis, A., Le, Q., Hinton, G., \& Dean, J. (2017). \emph{Outrageously Large Neural Networks: The Sparsely-Gated Mixture-of-Experts Layer}. \href{https://arxiv.org/abs/1701.06538}{arXiv:1701.06538}.

\item Shen, S., Hou, L., Zhou, Y., Du, N., Longpre, S., Wei, J., Chung, H. W., Zoph, B., Fedus, W., Chen, X., et al. (2023). \emph{Mixture-of-Experts Meets Instruction Tuning: A Winning Combination for Large Language Models}. \href{https://arxiv.org/abs/2305.14705}{arXiv:2305.14705}.

\item NVIDIA Developer Blog. (2023). \emph{Applying Mixture of Experts in LLM Architectures}. \href{https://developer.nvidia.com/blog/applying-mixture-of-experts-in-llm-architectures/}{developer.nvidia.com}.

\item Cai, W., Jiang, J., Wang, F., Tang, J., Kim, S., \& Huang, J. (2024). \emph{A Survey on Mixture of Experts in Large Language Models}. \href{https://arxiv.org/abs/2407.06204}{arXiv:2407.06204}.

\item DataCamp. (2024). \emph{What Is Mixture of Experts (MoE)? How It Works, Use Cases \& More}. \href{https://www.datacamp.com/blog/mixture-of-experts-moe}{datacamp.com}.

\item Dai, D., et al. (2023). \emph{Getting MoRE out of Mixture of Language Model Reasoning Experts}. In \emph{Findings of EMNLP 2023}. \href{https://aclanthology.org/2023.findings-emnlp.552.pdf}{ACL Anthology}.
\end{itemize}
\end{frame}
