% --- References ---
\begin{frame}[allowframebreaks]{References}
  \footnotesize
  \begin{enumerate}
    \item Vaswani et al., ``Attention Is All You Need,'' NeurIPS 2017. \href{https://arxiv.org/abs/1706.03762}{arXiv:1706.03762}
    \item Hinton, Vinyals, Dean, ``Distilling the Knowledge in a Neural Network,'' NIPS Deep Learning Workshop 2015. \href{https://arxiv.org/abs/1503.02531}{arXiv:1503.02531}
    \item Zelikman et al., ``STaR: Bootstrapping Reasoning With Reasoning,'' NeurIPS 2022. \href{https://arxiv.org/abs/2203.14465}{arXiv:2203.14465}
    \item Jacob et al., ``Quantization and Training of Neural Networks for Efficient Integer-Arithmetic-Only Inference,'' CVPR 2018. \href{https://arxiv.org/abs/1712.05877}{arXiv:1712.05877}
    \item Leviathan, Kalman, Matias, ``Fast Inference from Transformers via Speculative Decoding,'' ICML 2023. \href{https://arxiv.org/abs/2302.01318}{arXiv:2302.01318}
    \item Verma, ``Mastering LLM Techniques: Inference Optimization,'' NVIDIA Developer Blog, 17 Nov.\ 2023 (updated 15 Aug.\ 2024). \href{https://developer.nvidia.com/blog/mastering-llm-techniques-inference-optimization/}{Article}
    \item Wang, Spindler, ``Model Quantization: Concepts, Methods, and Why It Matters,'' NVIDIA Developer Blog, 24 Nov.\ 2025. \href{https://developer.nvidia.com/blog/model-quantization-concepts-methods-and-why-it-matters/}{Article}
    \item Zandieh, Daliri, Hadian, Mirrokni, ``TurboQuant: Online Vector Quantization with Near-optimal Distortion Rate,'' 2025. \href{https://arxiv.org/abs/2504.19874}{arXiv:2504.19874}
    \item Zandieh, Mirrokni, ``TurboQuant: Redefining AI efficiency with extreme compression,'' Google Research Blog, 24 Mar.\ 2026. \href{https://research.google/blog/turboquant-redefining-ai-efficiency-with-extreme-compression/}{Article}
    \item Khattab et al., \textit{LLM Class}: Lecture 1---Introduction and Course Overview (slide deck). \href{https://llm-class.github.io/slides/Lecture\%201\%20-\%20Introduction\%20and\%20Course\%20Overview.pdf}{PDF}
    \item Harvard University IACS, \textit{CS AC215---Advanced Practical Data Science} (Spring 2024), Lecture~11: \textit{Compression techniques} (slides 8--30 used for distillation figures). \href{https://harvard-iacs.github.io/2024-AC215/assets/lectures/lecture11/L11_compression_techniques.pdf}{PDF}
    \item CMU 15-779 (\textit{Lecture 17: LLM fine-tuning} --- slide deck). \href{https://www.cs.cmu.edu/\%7Ezhihaoj2/15-779/slides/17-LLM-finetuning.pdf}{PDF}
  \end{enumerate}
\end{frame}
