\section{References}
\begin{frame}[allowframebreaks]{}
    \LARGE Autoencoders: \textbf{References}
\end{frame}

\begin{frame}[allowframebreaks]{References}
\begin{thebibliography}{9}
\bibitem{bishop2006pattern}
Bishop, Christopher M. \emph{Pattern Recognition and Machine Learning}. Springer, 2006.

\bibitem{larochelle2011neural}
Larochelle, Hugo and Murray, Iain. ``Neural autoregressive distribution estimation.'' In \emph{AISTATS}, 2011, pp. 29--37.

\bibitem{uria2016neural}
Uria, Benigno, Murray, Iain, and Larochelle, Hugo. ``Neural Autoregressive Distribution Estimation.'' \emph{JMLR}, 17(205):1--37, 2016.

\bibitem{\begin{frame}[allowframebreaks]{References}
    \bibliographystyle{apalike}
    \begin{thebibliography}{99}
        \bibitem{hinton2006reducing}
        Hinton, G. E., \& Salakhutdinov, R. R. (2006).
        Reducing the dimensionality of data with neural networks.
        \textit{Science}, 313(5786), 504-507.

        \bibitem{vincent2008extracting}
        Vincent, P., Larochelle, H., Bengio, Y., \& Manzagol, P. A. (2008).
        Extracting and composing robust features with denoising autoencoders.
        In \textit{Proceedings of the 25th international conference on Machine learning} (pp. 1096-1103).

        \bibitem{kingma2013auto}
        Kingma, D. P., \& Welling, M. (2013).
        Auto-encoding variational Bayes.
        \textit{arXiv preprint arXiv:1312.6114}.

        \bibitem{makhzani2015adversarial}
        Makhzani, A., Shlens, J., Jaitly, N., Goodfellow, I., \& Frey, B. (2015).
        Adversarial autoencoders.
        \textit{arXiv preprint arXiv:1511.05644}.

        \bibitem{bengio2013representation}
        Bengio, Y., Courville, A., \& Vincent, P. (2013).
        Representation learning: A review and new perspectives.
        \textit{IEEE transactions on pattern analysis and machine intelligence}, 35(8), 1798-1828.

        \bibitem{baldi2012autoencoders}
        Baldi, P. (2012).
        Autoencoders, unsupervised learning, and deep architectures.
        In \textit{Proceedings of ICML Workshop on Unsupervised and Transfer Learning} (pp. 37-49).

        \bibitem{goodfellow2016deep}
        Goodfellow, I., Bengio, Y., \& Courville, A. (2016).
        Deep Learning.
        MIT Press.
    \end{thebibliography}
\end{frame}uria2013rnade}
Uria, Benigno, Murray, Iain, and Larochelle, Hugo. ``RNADE: The real-valued neural autoregressive density-estimator.'' In \emph{NeurIPS}, 2013, pp. 2175--2183.

\bibitem{oord2016pixelrnn}
van den Oord, Aaron, Kalchbrenner, Nal, and Kavukcuoglu, Koray. ``Pixel Recurrent Neural Networks.'' In \emph{ICML}, 2016, pp. 1747--1756.

\bibitem{oord2016pixelcnn}
van den Oord, Aaron, Kalchbrenner, Nal, and Kavukcuoglu, Koray. ``Conditional Image Generation with PixelCNN Decoders.'' In \emph{NeurIPS}, 2016, pp. 4790--4798.

\bibitem{oord2016wavenet}
van den Oord, Aaron, Dieleman, Sander, Zen, Heiga, Simonyan, Karen, Vinyals, Oriol, Graves, Alex, Kalchbrenner, Nal, Senior, Andrew, and Kavukcuoglu, Koray. ``WaveNet: A Generative Model for Raw Audio.'' \emph{arXiv preprint arXiv:1609.03499}, 2016.

\bibitem{salimans2017pixelcnnpp}
Salimans, Tim, Karpathy, Andrej, Chen, Xi, and Kingma, Diederik P. ``PixelCNN++: Improving the PixelCNN with Discretized Logistic Mixture Likelihood and Other Modifications.'' \emph{arXiv preprint arXiv:1701.05517}, 2017.
\end{thebibliography}
\end{frame}


\begin{frame}{}
	\LARGE VAE: \textbf{References}
\end{frame}

\begin{frame}[allowframebreaks]{References}
    Reference Slides
\begin{itemize}
    \item Fei-Fei Li "Generative Deep Learning" CS231
    \item Hao Dong "Deep Generative Models" 
    \item Hung-Yi Lee "Machine Learning" 
    \item Murtaza Taj "Deep Learning" CS437
    \item Aykut Erdem, \href{https://aykuterdem.github.io/classes/comp547.s24/}{COMP547: Deep Unsupervised Learning, Koc University}

\end{itemize}

\framebreak
    \frametitle{References}
    \begin{thebibliography}{99}
        \bibitem{Kingma2013}
        D. P. Kingma and M. Welling,
        \newblock "Auto-Encoding Variational Bayes,"
        \newblock \emph{arXiv preprint arXiv:1312.6114}, 2013.

        \bibitem{Rezende2014}
        D. J. Rezende, S. Mohamed, and D. Wierstra,
        \newblock "Stochastic Backpropagation and Approximate Inference in Deep Generative Models,"
        \newblock \emph{Proceedings of the 31st International Conference on Machine Learning (ICML)}, 2014.

        \bibitem{Higgins2017}
        I. Higgins, L. Matthey, A. Pal, et al.,
        \newblock "beta-VAE: Learning Basic Visual Concepts with a Constrained Variational Framework,"
        \newblock \emph{International Conference on Learning Representations (ICLR)}, 2017.

        \bibitem{Burgess2018}
        C. P. Burgess, I. Higgins, A. Pal, et al.,
        \newblock "Understanding Disentangling in $\beta$-VAE,"
        \newblock \emph{arXiv preprint arXiv:1804.03599}, 2018.

        \bibitem{Kingma2016}
        D. P. Kingma, T. Salimans, R. Jozefowicz, et al.,
        \newblock "Improved Variational Inference with Inverse Autoregressive Flow,"
        \newblock \emph{Advances in Neural Information Processing Systems (NeurIPS)}, 2016.

        \bibitem{VQ-VAE}
        A. van den Oord, O. Vinyals, and K. Kavukcuoglu,
        \newblock "Neural Discrete Representation Learning,"
        \newblock \emph{Advances in Neural Information Processing Systems (NeurIPS)}, 2017.

        \bibitem{Higgins2018}
        I. Higgins, D. Amos, D. Pfau, et al.,
        \newblock "Towards a Definition of Disentangled Representations,"
        \newblock \emph{arXiv preprint arXiv:1812.02230}, 2018.

        \bibitem{Doersch2016}
        C. Doersch,
        \newblock "Tutorial on Variational Autoencoders,"
        \newblock \emph{arXiv preprint arXiv:1606.05908}, 2016.

        \bibitem{Blei2017}
        D. M. Blei, A. Kucukelbir, and J. D. McAuliffe,
        \newblock "Variational Inference: A Review for Statisticians,"
        \newblock \emph{Journal of the American Statistical Association}, 2017.
    \end{thebibliography}
\end{frame}