\section{References}
\begin{frame}{References}
  These slides have been adapted from:
  \begin{itemize}
    \item[$\blacktriangleright$] Younes Mourri \& Lukasz Kaiser, \href{https://www.deeplearning.ai/program/natural-language-processing/}{Natural Language Processing Specialization, DeepLearning.AI}
    \item[$\blacktriangleright$] Bhiksha Raj \& Rita Singh, \href{https://www.cs.cmu.edu/~10785/}{11-785 Introduction to Deep Learning, CMU}
  \end{itemize}
\end{frame}

\section{References}
\begin{frame}{References}
  \textbf{Foundational Papers:}
  \begin{itemize}
    \item[$\blacktriangleright$] Sutskever et al.\ (2014). \textit{Sequence to Sequence Learning with Neural Networks}. NeurIPS.
    \item[$\blacktriangleright$] Bahdanau et al.\ (2014). \textit{Neural Machine Translation by Jointly Learning to Align and Translate}.
    \item[$\blacktriangleright$] Luong et al.\ (2015). \textit{Effective Approaches to Attention-based Neural Machine Translation}.
    \item[$\blacktriangleright$] Vaswani et al.\ (2017). \textit{Attention Is All You Need} (Transformer).
    \item[$\blacktriangleright$] Chan et al.\ (2016). \textit{Listen, Attend and Spell} (Speech recognition).
  \end{itemize}
\end{frame}

\section{References}
\begin{frame}{References}
  \textbf{Courses \& Tutorials:}
  \begin{itemize}
    \item[$\blacktriangleright$] Stanford CS224n: Lecture 9 (Attention)
    \item[$\blacktriangleright$] DeepLearning.ai NLP Specialization (Coursera)
    \item[$\blacktriangleright$] Harvard NLP Annotated Transformer:\\
      \texttt{\color{magenta}http://nlp.seas.harvard.edu/2018/04/03/attention.html}
    \item[$\blacktriangleright$] Jay Alammar's blog: ``The Illustrated Transformer''
  \end{itemize}
\end{frame}