\begin{frame}[allowframebreaks]{}
    \centering
    \LARGE Autoregressive Models: \textbf{Historical Models}
\end{frame}

\begin{frame}[allowframebreaks]{Historical Models}
    Before models like \textbf{Transformers} and \textbf{PixelCNN}, some key neural autoregressive models laid 
    the groundwork for using neural networks to estimate data distributions. \\
    Here’s a quick overview:

    \begin{itemize}
        \item \textbf{FVSBN (Fully Visible Sigmoid Belief Networks):} 
        One of the first models to break down complex data into simpler parts, making it easier to calculate probabilities.
        \item \textbf{NADE (Neural Autoregressive Distribution Estimator):} 
        Used neural networks to model binary data step by step, making the process efficient and scalable.
        \item \textbf{RNADE (Real-valued NADE):} 
        Extended NADE to work with real numbers, so it could handle more types of data.
    \end{itemize}

    These early models showed that neural networks could be used for density estimation and inspired many of the advanced models we use today.
\end{frame}

\input{sections/autoregressive/historical_models/fvsbn}
\input{sections/autoregressive/historical_models/nade}

\begin{frame}{Non-Binary Outputs}
    \begin{itemize}
        \item What if the output variable is not binary? For example, we have to predict pixel value between 0 and 255.
        \item One solution: Let $\mathbf{\hat{x}}_i$ parameterize a categorical distribution
        \begin{align}
            h_i = \sigma(\mathbf{W}_{.,<i} x_{<i} + c)\\
            \mathcal{P}(x_i | x_1, \cdots, x_{i-1}) = \text{Cat}(p_i^1, \cdots, p_i^K)\\
            \mathbf{\hat{x}}_i = (p_i^1, \cdots, p_i^K) = \text{softmax} (A_i h_i + b_i)
        \end{align}
        \item Softmax generalizes the sigmoid function $\sigma(\cdot)$ and transforms a vector of K numbers into a vector of K probabilities (non-negative, sum to 1).

    \end{itemize}
\end{frame}

\input{sections/autoregressive/historical_models/rnade}
\input{sections/autoregressive/historical_models/learning-rnn}
\input{sections/autoregressive/historical_models/pixel-rnn}