\begin{frame}{}
    \centering
    \LARGE Autoregressive Models: \textbf{Modern Models}
\end{frame}

\begin{frame}[allowframebreaks]{Autoregressive Models: Modern Models}
    Modern autoregressive models are powerful tools for generating data like images, audio, and text. Let’s look at some popular ones and why they matter:

    \begin{itemize}
        \item \textbf{PixelCNN/PixelSNAIL:} Great for generating images, using special convolutions to look at pixels one by one.
        \item \textbf{WaveNet:} Designed for audio, it can create realistic speech and music by looking at sound samples in order.
        \item \textbf{Transformer-based Models:} Used in language models like GPT, these use attention to understand and generate sequences (text, images, etc.).
    \end{itemize}

    \framebreak

    \textbf{PixelCNN/PixelSNAIL:}
    \begin{itemize}
        \item PixelCNN was introduced in 2016 to generate images pixel by pixel.
        \item It uses masked convolutions so each pixel only depends on the ones before it.
        \item PixelSNAIL improves on this by adding attention, helping the model see more of the image at once.
        \item Both are good at making realistic images.
    \end{itemize}

    \framebreak

    \textbf{WaveNet:}
    \begin{itemize}
        \item WaveNet was made for audio generation, like speech and music.
        \item It uses dilated convolutions to look at long stretches of audio.
        \item Each sound sample depends on the previous ones, making the output sound natural.
        \item WaveNet set new standards for speech synthesis.
    \end{itemize}

    \framebreak

    \textbf{Transformer-based Models:}
    \begin{itemize}
        \item Transformers were introduced in 2017 for language tasks.
        \item They use self-attention to look at all parts of a sequence at once.
        \item This makes them fast and good at handling long texts or sequences.
        \item Famous models like GPT-3 and BERT use this idea.
        \item Transformers can also be used for images and audio, not just text.
    \end{itemize}

    \framebreak

    \textbf{Applications:}
    \begin{itemize}
        \item Making new images (PixelCNN, PixelSNAIL)
        \item Generating speech and music (WaveNet)
        \item Writing text and language modeling (Transformers)
        \item Creating videos and working with multiple types of data
    \end{itemize}

    \framebreak

    \textbf{Pros:}
    \begin{itemize}
        \item Can generate high-quality images, audio, and text
        \item Good at learning complex patterns in data
        \item Scalable to large datasets and tasks
    \end{itemize}

    \textbf{Cons:}
    \begin{itemize}
        \item Training and running these models can be expensive
        \item Need lots of data to work well
        \item Still challenging for very large or complex data
    \end{itemize}
\end{frame}
\input{sections/autoregressive/modern_models/pixelcnn}
\input{sections/autoregressive/modern_models/wavenet}