\begin{frame}[allowframebreaks]{}
    \centering
    \LARGE References
\end{frame}

\begin{frame}[allowframebreaks]{References}
\begin{thebibliography}{9}
\bibitem{bishop2006pattern}
Bishop, Christopher M. \emph{Pattern Recognition and Machine Learning}. Springer, 2006.

\bibitem{larochelle2011neural}
Larochelle, Hugo and Murray, Iain. ``Neural autoregressive distribution estimation.'' In \emph{AISTATS}, 2011, pp. 29--37.

\bibitem{uria2016neural}
Uria, Benigno, Murray, Iain, and Larochelle, Hugo. ``Neural Autoregressive Distribution Estimation.'' \emph{JMLR}, 17(205):1--37, 2016.

\bibitem{uria2013rnade}
Uria, Benigno, Murray, Iain, and Larochelle, Hugo. ``RNADE: The real-valued neural autoregressive density-estimator.'' In \emph{NeurIPS}, 2013, pp. 2175--2183.

\bibitem{oord2016pixelrnn}
van den Oord, Aaron, Kalchbrenner, Nal, and Kavukcuoglu, Koray. ``Pixel Recurrent Neural Networks.'' In \emph{ICML}, 2016, pp. 1747--1756.

\bibitem{oord2016pixelcnn}
van den Oord, Aaron, Kalchbrenner, Nal, and Kavukcuoglu, Koray. ``Conditional Image Generation with PixelCNN Decoders.'' In \emph{NeurIPS}, 2016, pp. 4790--4798.

\bibitem{oord2016wavenet}
van den Oord, Aaron, Dieleman, Sander, Zen, Heiga, Simonyan, Karen, Vinyals, Oriol, Graves, Alex, Kalchbrenner, Nal, Senior, Andrew, and Kavukcuoglu, Koray. ``WaveNet: A Generative Model for Raw Audio.'' \emph{arXiv preprint arXiv:1609.03499}, 2016.

\bibitem{salimans2017pixelcnnpp}
Salimans, Tim, Karpathy, Andrej, Chen, Xi, and Kingma, Diederik P. ``PixelCNN++: Improving the PixelCNN with Discretized Logistic Mixture Likelihood and Other Modifications.'' \emph{arXiv preprint arXiv:1701.05517}, 2017.
\end{thebibliography}
\end{frame}

