\begin{frame}{}
    \LARGE Object Detection: \textbf{References \& Resources}
\end{frame}

\begin{frame}[allowframebreaks]{References \& Resources}
    \begin{thebibliography}{99}
        \bibitem{rcnn}
            R-CNN to Faster R-CNN: Girshick et al. 2014–2015 \\
            R-CNN: \url{https://arxiv.org/abs/1311.2524} \\
            Fast R-CNN: \url{https://arxiv.org/abs/1504.08083} \\
            Faster R-CNN: \url{https://arxiv.org/abs/1506.01497}
        \bibitem{maskrcnn}
            Mask R-CNN: He et al. (2017) \\
            \url{https://arxiv.org/abs/1703.06870}
        \bibitem{yolo-original}
            YOLO Original Series (v1–v3): Redmon et al. \\
            YOLOv1: \url{https://arxiv.org/abs/1506.02640} \\
            YOLOv2: \url{https://arxiv.org/abs/1612.08242} \\
            YOLOv3: \url{https://pjreddie.com/media/files/papers/YOLOv3.pdf}
        \bibitem{yolov4}
            YOLOv4: Bochkovskiy et al. 2020 \\
            \url{https://arxiv.org/abs/2004.10934}
        \bibitem{yolov5}
            YOLOv5: Ultralytics (2020) \\
            \url{https://github.com/ultralytics/yolov5}
        \bibitem{yolov6}
            YOLOv6: Li et al. (2022) \\
            \url{https://arxiv.org/abs/2209.02976}
        \bibitem{yolov7}
            YOLOv7: Wang et al. (2022) \\
            \url{https://arxiv.org/abs/2207.02696}
        \bibitem{yolov8}
            YOLOv8: Ultralytics (2023) \\
            \url{https://github.com/ultralytics/ultralytics}
        \bibitem{yolov10}
            YOLOv10: Wang et al. (May 2024) \\
            \url{https://arxiv.org/abs/2405.12345} % Placeholder, update with actual link if available
        \bibitem{yolov11}
            YOLOv11: Architectural update Sept 2024
        \bibitem{yolov12}
            YOLOv12: Attention-centric Feb 2025
        \bibitem{mambanext}
            MambaNeXt-YOLO (June 2025)
        \bibitem{rtdetr}
            RT-DETR: Zhao et al. (April 2023) \\
            \url{https://arxiv.org/abs/2304.08069}
        \bibitem{detr}
            DETR (Transformers): \url{https://arxiv.org/abs/2005.12872}
        \bibitem{yoloworld}
            YOLO-World zero-shot model \\
            \url{https://arxiv.org/abs/2311.15620}
        \bibitem{cs231n}
            Fei-Fei Li, Yunzhu Li \& Ruohan Gao, Stanford CS231n: Deep Learning for Computer Vision \\
            \url{http://cs231n.stanford.edu/}
        \bibitem{waic-dl4cv}
            Assaf Shocher, Shai Bagon, Meirav Galun \& Tali Dekel, WAIC DL4CV Deep Learning for Computer Vision: Fundamentals and Applications \\
            \url{https://www.weizmann.ac.il/math/AssafShocher/WAIC-DL4CV/}
        \bibitem{umich-dl4cv}
            Justin Johnson, UMich EECS 498.008/598.008: Deep Learning for Computer Vision \\
            \url{https://web.eecs.umich.edu/~justincj/teaching/eecs498/}
    \end{thebibliography}
    \frametitle{Explore Open Source}
    \begin{itemize}
        \item \url{https://github.com/pjreddie/darknet}
        \item \url{https://github.com/ultralytics/yolov5}
        \item \url{https://github.com/facebookresearch/detectron2}
        \item \url{https://github.com/ultralytics/ultralytics}
    \end{itemize}
    \frametitle{Further Reading}
    \begin{itemize}
        \item Wikipedia: \url{https://en.wikipedia.org/wiki/You_Only_Look_Once}
        \item Springer: \url{https://link.springer.com/article/10.1007/s11263-015-0816-y}
        \item Reddit: \url{https://www.reddit.com/r/MachineLearning/}
        \item CapaLearning: \url{https://capalearning.com/}
    \end{itemize}
\end{frame}