\section{References}
\begin{frame}{}
    \LARGE Image and Video Captioning: \textbf{References}
\end{frame}

\begin{frame}[allowframebreaks]{References}
\begin{thebibliography}{99}

\bibitem{vinyals2015show}
Vinyals, O., Toshev, A., Bengio, S., \& Erhan, D.
\newblock Show and Tell: A Neural Image Caption Generator.
\newblock In \emph{CVPR}, 2015.
\newblock \url{https://arxiv.org/abs/1411.4555}

\bibitem{radford2021clip}
Radford, A., Kim, J. W., Hallacy, C., Ramesh, A., Goh, G., Agarwal, S., Sastry, G., Askell, A., Mishkin, P., Clark, J., Krueger, G., \& Sutskever, I.
\newblock Learning Transferable Visual Models From Natural Language Supervision (CLIP).
\newblock In \emph{ICML}, 2021.
\newblock \url{https://arxiv.org/abs/2103.00020}

\bibitem{ramesh2022dalle2}
Ramesh, A., Dhariwal, P., Nichol, A., Chu, C., \& Chen, M.
\newblock Hierarchical Text-Conditional Image Generation with CLIP Latents (DALL-E 2).
\newblock \emph{arXiv preprint}, 2022.
\newblock \url{https://arxiv.org/abs/2204.06125}

\bibitem{rombach2022ldm}
Rombach, R., Blattmann, A., Lorenz, D., Esser, P., \& Ommer, B.
\newblock High-Resolution Image Synthesis with Latent Diffusion Models (Stable Diffusion).
\newblock In \emph{CVPR}, 2022.
\newblock \url{https://arxiv.org/abs/2112.10752}

\bibitem{saharia2022imagen}
Saharia, C., Chan, W., Saxena, S., Li, L., Whang, J., Denton, E., Salimans, T., Ho, J., Fleet, D. J., \& Norouzi, M.
\newblock Photorealistic Text-to-Image Diffusion Models with Deep Language Understanding (Imagen).
\newblock In \emph{NeurIPS}, 2022.
\newblock \url{https://arxiv.org/abs/2205.11487}

\bibitem{blip}
BLIP: Bootstrapped Language-Image Pretraining.
\newblock \url{https://github.com/salesforce/BLIP}

\bibitem{dalle2}
OpenAI's DALL\textbullet E 2 Documentation.
\newblock \url{https://platform.openai.com/docs/guides/images}

\bibitem{midjourney}
Midjourney Documentation.
\newblock \url{https://docs.midjourney.com/}

\bibitem{sdxl}
SDXL (Stable Diffusion XL) Documentation.
\newblock \url{https://stability.ai/guides/sdxl}

\end{thebibliography}
\end{frame}