\begin{frame}{}
    \LARGE Advanced Diffusion Models: \textbf{Fine-Tuning}
\end{frame}

\begin{frame}[allowframebreaks]{Fine-Tuning Diffusion Models}

\vspace{1em}
\begin{itemize}
    \item Fine-tuning lets you teach a diffusion model new things using your own images.
    \item You can make the model generate pictures in your style or for your special needs.
    \item Just use a few of your own photos—like products, anime, or anything unique to you.
    \item This way, the model becomes more useful and personal for your projects.
\end{itemize}

\end{frame}

\begin{frame}[allowframebreaks]{Why Fine-Tune?}
\begin{itemize}
    \item \textbf{Customization:} Generate images that reflect your brand, style, or unique requirements.
    \item \textbf{Personalization:} Learn your own visual style, such as custom portraits, branding elements, or new characters.
    \item \textbf{Domain Adaptation:} Improve performance on niche or underrepresented domains.
\end{itemize}
\end{frame}

\begin{frame}[allowframebreaks]{Popular Fine-Tuning Methods}
\begin{itemize}
    \item \textbf{DreamBooth:}
    \begin{itemize}
        \item Enables the model to learn new concepts from a small set of images.
        \item Useful for injecting specific subjects or styles into the model.
        \item Lightweight and efficient—requires only a few images and limited compute.
    \end{itemize}
    \item \textbf{LoRA (Low-Rank Adaptation):}
    \begin{itemize}
        \item Introduces trainable low-rank matrices into the model.
        \item Allows efficient fine-tuning with minimal changes to the original weights.
        \item Reduces memory and compute requirements.
    \end{itemize}
\end{itemize}
\end{frame}

\input{sections/adv-img-gen/finetuning/dreambooth}
\input{sections/adv-img-gen/finetuning/lora}

\begin{frame}[allowframebreaks]{Applications of Fine-Tuning}
\begin{itemize}
    \item \textbf{Portrait Generation:} Create personalized avatars or stylized portraits.
    \item \textbf{Branding:} Generate images consistent with your brand's visual identity.
    \item \textbf{Character Design:} Develop new characters for games, comics, or animation.
    \item \textbf{Product Imagery:} Produce custom product images for marketing or e-commerce.
\end{itemize}
\end{frame}
