\begin{frame}{}
    \LARGE Advanced Diffusion Models: \textbf{References}
\end{frame}

\begin{frame}[allowframebreaks]{References}
    \bibliographystyle{ieeetr}
    \begin{thebibliography}{99}

    \bibitem{rombach2022latent}
    Rombach, Robin, Andreas Blattmann, Dominik Lorenz, Patrick Esser, and Björn Ommer. "High-resolution image synthesis with latent diffusion models." In \textit{Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition}, pp. 10684-10695. 2022.

    \bibitem{song2021score}
    Song, Yang, Jascha Sohl-Dickstein, Diederik P. Kingma, Abhishek Kumar, Stefano Ermon, and Ben Poole. "Score-based generative modeling through stochastic differential equations." In \textit{International Conference on Learning Representations (ICLR)}, 2021.

    \bibitem{ruiz2023dreambooth}
    Ruiz, Nataniel, Yuanzhen Li, Varun Jampani, Yael Pritch, Michael Rubinstein, and Kfir Aberman. "DreamBooth: Fine Tuning Text-to-Image Diffusion Models for Subject-Driven Generation." In \textit{arXiv preprint arXiv:2208.12242}, 2022.

    \bibitem{hu2021lora}
    Hu, Edward J., Yelong Shen, Phillip Wallis, Zeyuan Allen-Zhu, Yuanzhi Li, Shean Wang, Lu Wang, and Weizhu Chen. "LoRA: Low-Rank Adaptation of Large Language Models." In \textit{arXiv preprint arXiv:2106.09685}, 2021.

    \bibitem{saharia2022imagen}
    Saharia, Chitwan, William Chan, Saurabh Saxena, Lala Li, Jay Whang, Emily Denton, Seyed Kamyar Seyed Ghasemipour et al. "Photorealistic text-to-image diffusion models with deep language understanding." In \textit{arXiv preprint arXiv:2205.11487}, 2022.

    \bibitem{ramesh2022hierarchical}
    Ramesh, Aditya, Prafulla Dhariwal, Alex Nichol, Casey Chu, and Mark Chen. "Hierarchical text-conditional image generation with clip latents." In \textit{arXiv preprint arXiv:2204.06125}, 2022.

    \bibitem{cs294-158}
    Abbeel, Pieter, Wilson Yan, Kevin Frans, and Philipp Wu. "CS294-158 Deep Unsupervised Learning, Lecture 6: Diffusion Models." UC Berkeley, 2022. \url{https://rail.eecs.berkeley.edu/deeprlcourse-fa22/static/notes/lec6.pdf}

    \end{thebibliography}
\end{frame}