\begin{frame}{}
    \LARGE GANs: \textbf{Variants}
\end{frame}

\begin{frame}[allowframebreaks]{GAN Variants}
\begin{itemize}
    \item Since the introduction of GANs, extensive research has led to many variants.
    \item A comprehensive list of GAN variants can be found \href{https://github.com/hindupuravinash/the-gan-zoo}{here}.
\end{itemize} 
    \framebreak
    
    We will discuss the following variants:
    \begin{itemize}
        \item \textbf{Deep Convolutional GAN (DCGAN):}
        \begin{itemize}
            \item Uses convolutional and transposed convolutional layers.
            \item Employs batch normalization and ReLU/LeakyReLU activations.
            \item Improves training stability and image quality.
        \end{itemize}
        \item \textbf{Wasserstein GAN (WGAN):} 
        \begin{itemize}
            \item Introduces Wasserstein distance as the objective.
            \item Replaces sigmoid with linear output.
            \item Uses weight clipping or gradient penalty.
            \item \textbf{Variants:}
            \begin{itemize}
                \item \textbf{WGAN-GP:} Uses gradient penalty instead of weight clipping for better stability.
                \item \textbf{WGAN-LP:} Uses Lipschitz penalty as an alternative to gradient penalty.
            \end{itemize}
        \end{itemize}

\framebreak

        \item \textbf{Conditional GAN (cGAN):} 
        \begin{itemize}
            \item Conditions both the generator and discriminator on additional information (e.g., class labels).
            \item Useful for targeted generation.
        \end{itemize}
        \item \textbf{CycleGAN:} 
        \begin{itemize}
            \item Enables unpaired image-to-image translation.
            \item Uses cycle consistency loss to ensure invertibility.
        \end{itemize}
        \item \textbf{StyleGAN:} 
        \begin{itemize}
            \item Developed by NVIDIA for high-fidelity face generation.
            \item Introduces style vectors at each generator layer.
            \item Allows fine-grained control over image features.
        \end{itemize}
    \end{itemize}
\end{frame}

\input{sections/gan/variants/deep_convolutional_gans}
\input{sections/gan/variants/wasserstein_gans}
\input{sections/gan/variants/conditional_gans}
\input{sections/gan/variants/cyclegans}
\input{sections/gan/variants/stylegans}