% Includes second thebibliography block as in Lecture-10 (lines 746--769).
\begin{frame}[allowframebreaks]{References}
  \small
  \begin{thebibliography}{10}
    \bibitem{radford2021clip}
      Radford, A., Kim, J. W., Hallacy, C., et al. (2021). \\
      \emph{CLIP: Learning Transferable Visual Models From Natural Language Supervision}.\\
      \href{https://arxiv.org/abs/2103.00020}{arXiv:2103.00020}

    \bibitem{li2019visualbert}
      Li, L. H., Yatskar, M., Yin, D., Hsieh, C. J., Chang, K. W. (2019). \\
      \emph{VisualBERT: A Simple and Performant Baseline for Vision and Language}.\\
      \href{https://arxiv.org/abs/1908.03557}{arXiv:1908.03557}

    \bibitem{singh2021flava}
      Singh, A., Goyal, N., Goswami, V., et al. (2021). \\
      \emph{FLAVA: A Foundational Language And Vision Alignment Model}.\\
      \href{https://arxiv.org/abs/2112.04482}{arXiv:2112.04482}

    \bibitem{yao2023react}
      Yao, S., Zhao, J., Yu, D., et al. (2023). \\
      \emph{ReAct: Synergizing Reasoning and Acting in Language Models}.\\
      \href{https://arxiv.org/abs/2210.03629}{arXiv:2210.03629}
  \end{thebibliography}
\end{frame}

  % Additional references
  \begin{thebibliography}{10}
    \setcounter{enumiv}{4} % Continue from previous bibliography if needed

    \bibitem{nakajima2023babyagi}
      Nakajima, Y. (2023). \\
      BabyAGI.\\
      \href{https://github.com/yoheinakajima/babyagi}{https://github.com/yoheinakajima/babyagi}

    \bibitem{torantulino2023autogpt}
      Torantulino (2023). \\
      Auto-GPT.\\
      \href{https://github.com/Torantulino/Auto-GPT}{https://github.com/Torantulino/Auto-GPT}

    \bibitem{ahn2022say}
      Ahn, M., Brohan, A., Chebotar, Y., et al. (2022). \\
      Do As I Can, Not As I Say: Grounding Language in Robotic Affordances.\\
      \emph{arXiv:2204.01691}.

    \bibitem{openai_superalignment}
      OpenAI Blog. \\
      Agent Simulations and Superalignment.\\
      \href{https://openai.com/blog/}{https://openai.com/blog/}
  \end{thebibliography}
