\begin{frame}{}
    \LARGE Generative AI for Science: \textbf{References}
\end{frame}

\begin{frame}[allowframebreaks]{References}
    \begin{itemize}
        \item AlphaFold: Jumper, J., Evans, R., Pritzel, A., Green, T., Figurnov, M., Ronneberger, O., ... \& Hassabis, D. (2021). Highly accurate protein structure prediction with AlphaFold. Nature, 596(7873), 583-589.
        \item Earth-2: NVIDIA. (2022). Earth-2: A Digital Twin of the Earth for Climate Research. Retrieved from \url{https://www.nvidia.com/en-us/research/earth-2/}
        \item SMILES: Weininger, D. (1988). SMILES, a chemical language and information system. 1. Introduction to methodology and encoding rules. Journal of Chemical Information and Computer Sciences, 28(1), 31-36.
    \end{itemize}
    \framebreak
    \begin{itemize}
        \item FourCastNet: Salazar, J., & Koster, R. D. (2021). FourCastNet: A global data-driven high-resolution weather model. Nature, 591(7849), 234-239.
        \item ChemDFM: Zhang, Y., Wang, H., & Liu, B. (2023). ChemDFM: A foundation model for chemistry. Cell, 186(1), 1-15.
        \item Science Advances: Chen, H., & Zhang, Y. (2023). Leveraging negative reactions for improved reactivity predictions. Science Advances, 9(12), eadk1426.
    \end{itemize}
    \framebreak
    \textbf{Additional Resources:}
    \begin{itemize}
        \item NVIDIA Earth-2: \url{https://build.nvidia.com/nvidia/fourcastnet?snippet_tab=Try}
        \item SMILES: \url{https://www.daylight.com/dayhtml/doc/theory/theory.smiles.html}
        \item AlphaFold: \url{https://alphafold.ebi.ac.uk/}
        \item Earth-2: \url{https://www.nvidia.com/en-us/research/earth-2/}
    \end{itemize}
\end{frame}