\begin{frame}{}
	\LARGE VAE: \textbf{References}
\end{frame}

\begin{frame}[allowframebreaks]{References}
    Reference Slides
\begin{itemize}
    \item Fei-Fei Li "Generative Deep Learning" CS231
    \item Hao Dong "Deep Generative Models" 
    \item Hung-Yi Lee "Machine Learning" 
    \item Murtaza Taj "Deep Learning" CS437
    \item Aykut Erdem, \href{https://aykuterdem.github.io/classes/comp547.s24/}{COMP547: Deep Unsupervised Learning, Koc University}

\end{itemize}

\framebreak
    \frametitle{References}
    \begin{thebibliography}{99}
        \bibitem{Kingma2013}
        D. P. Kingma and M. Welling,
        \newblock "Auto-Encoding Variational Bayes,"
        \newblock \emph{arXiv preprint arXiv:1312.6114}, 2013.

        \bibitem{Rezende2014}
        D. J. Rezende, S. Mohamed, and D. Wierstra,
        \newblock "Stochastic Backpropagation and Approximate Inference in Deep Generative Models,"
        \newblock \emph{Proceedings of the 31st International Conference on Machine Learning (ICML)}, 2014.

        \bibitem{Higgins2017}
        I. Higgins, L. Matthey, A. Pal, et al.,
        \newblock "beta-VAE: Learning Basic Visual Concepts with a Constrained Variational Framework,"
        \newblock \emph{International Conference on Learning Representations (ICLR)}, 2017.

        \bibitem{Burgess2018}
        C. P. Burgess, I. Higgins, A. Pal, et al.,
        \newblock "Understanding Disentangling in $\beta$-VAE,"
        \newblock \emph{arXiv preprint arXiv:1804.03599}, 2018.

        \bibitem{Kingma2016}
        D. P. Kingma, T. Salimans, R. Jozefowicz, et al.,
        \newblock "Improved Variational Inference with Inverse Autoregressive Flow,"
        \newblock \emph{Advances in Neural Information Processing Systems (NeurIPS)}, 2016.

        \bibitem{VQ-VAE}
        A. van den Oord, O. Vinyals, and K. Kavukcuoglu,
        \newblock "Neural Discrete Representation Learning,"
        \newblock \emph{Advances in Neural Information Processing Systems (NeurIPS)}, 2017.

        \bibitem{Higgins2018}
        I. Higgins, D. Amos, D. Pfau, et al.,
        \newblock "Towards a Definition of Disentangled Representations,"
        \newblock \emph{arXiv preprint arXiv:1812.02230}, 2018.

        \bibitem{Doersch2016}
        C. Doersch,
        \newblock "Tutorial on Variational Autoencoders,"
        \newblock \emph{arXiv preprint arXiv:1606.05908}, 2016.

        \bibitem{Blei2017}
        D. M. Blei, A. Kucukelbir, and J. D. McAuliffe,
        \newblock "Variational Inference: A Review for Statisticians,"
        \newblock \emph{Journal of the American Statistical Association}, 2017.
    \end{thebibliography}
\end{frame}