% % --- References (curated from SSL/JEPA lecture-resources report “Works cited”) ---
\begin{frame}[allowframebreaks]{References}
  \footnotesize
  \begin{enumerate}\itemsep0.08em
    \item Assran et al., ``Self-Supervised Learning from Images with a Joint-Embedding Predictive Architecture,'' ICLR 2023. \href{https://arxiv.org/abs/2301.08243}{arXiv:2301.08243}
    \item Bardes et al., ``Revisiting Feature Prediction for Learning Visual Representations from Video,'' 2024. \href{https://arxiv.org/abs/2404.08471}{arXiv:2404.08471}
    \item LeCun, ``A Path Towards Autonomous Machine Intelligence,'' OpenReview 2022. \href{https://openreview.net/forum?id=BZ5a1r-kVsf}{OpenReview}
    \item Meta AI, ``I-JEPA: The first AI model based on Yann LeCun's vision for more human-like AI,'' \emph{AI at Meta} blog, 2023. \href{https://ai.meta.com/blog/yann-lecun-ai-model-i-jepa}{ai.meta.com}
    \item Meta AI, ``Yann LeCun on a vision to make AI systems learn and reason like animals and humans,'' \emph{AI at Meta} blog. \href{https://ai.meta.com/blog/yann-lecun-advances-in-ai-research/}{ai.meta.com}
    \item Meta AI, ``Introducing V-JEPA 2,'' V-JEPA research hub. \href{https://ai.meta.com/research/vjepa/}{ai.meta.com/research/vjepa}
    \item Assran et al., ``V-JEPA 2: Self-Supervised Video Models Enable Understanding, Prediction and Planning,'' 2025. \href{https://arxiv.org/abs/2506.09985}{arXiv:2506.09985}
    \item ``Tutorial on Joint Embedding Predictive Architectures (JEPA),'' TechRxiv. \href{https://www.techrxiv.org/doi/10.36227/techrxiv.176469421.19270944}{DOI:10.36227/techrxiv.176469421.19270944}
    \item Kalapos \& Gyires-Tóth, ``CNN-JEPA: Self-Supervised Pretraining Convolutional Neural Networks Using Joint Embedding Predictive Architecture,'' 2024. \href{https://arxiv.org/abs/2408.07514}{arXiv:2408.07514}
    \item Saito et al., ``Point-JEPA: A Joint Embedding Predictive Architecture for Self-Supervised Learning on Point Cloud,'' 2024. \href{https://arxiv.org/abs/2404.16432}{arXiv:2404.16432}
    \item Wu et al., ``Sonata: Self-Supervised Learning of Reliable Point Representations,'' CVPR 2025. \href{https://arxiv.org/abs/2503.16429}{arXiv:2503.16429}
    \item Li et al., ``Rethinking JEPA: Compute-Efficient Video SSL with Frozen Teachers'' (SALT), Apple ML Research, 2025. \href{https://arxiv.org/abs/2509.24317}{arXiv:2509.24317}
    \item Khan et al., ``A Survey of the Self Supervised Learning Mechanisms for Vision Transformers,'' 2024. \href{https://arxiv.org/abs/2408.17059}{arXiv:2408.17059}
    \item Meta AI, ``V-JEPA: The next step toward advanced machine intelligence,'' \emph{AI at Meta} blog, 2024. \href{https://ai.meta.com/blog/v-jepa-yann-lecun-ai-model-video-joint-embedding-predictive-architecture/}{ai.meta.com}
    \item He et al., ``Masked Autoencoders Are Scalable Vision Learners,'' CVPR 2022.
    \item Baevski et al., ``data2vec: A General Framework for Self-supervised Learning in Speech, Vision and Language,'' ICML 2022.
    \item Chen et al., ``A Simple Framework for Contrastive Learning of Visual Representations (SimCLR),'' ICML 2020.
    \item Devlin et al., ``BERT,'' NAACL 2019.
    \item Touvron et al., ``An Image is Worth 16x16 Words (ViT),'' ICLR 2021.
    \item Stanford CS231n, Lecture 12 slides (SSL). \href{https://cs231n.stanford.edu/2024/slides/2024/lecture_12.pdf}{PDF}
    \item UC Berkeley CS294-158 (SP20), Deep Unsupervised Learning. \href{https://sites.google.com/view/berkeley-cs294-158-sp20/home}{course site}
    \item CMU 11-785 Deep Learning. \href{https://deeplearning.cs.cmu.edu/}{deeplearning.cs.cmu.edu}
    \item MIT 6.S191 Introduction to Deep Learning. \href{https://introtodeeplearning.com/}{introtodeeplearning.com}
    \item Kuka, V., ``What is JEPA?'' \emph{Turing Post}, 2024. \href{https://www.turingpost.com/p/jepa}{turingpost.com}
    \item LeCun, Les Houches lecture slides (AMI / world models). \href{https://leshouches2022.github.io/SLIDES/lecun-20220720-leshouches-03.pdf}{PDF}
  \end{enumerate}
\end{frame}
