\begin{frame}{References}
  \footnotesize
  \begin{enumerate}
    \item Ouyang, L., Wu, J., Jiang, X., et al. (2022). Training language models to follow instructions with human feedback. InstructGPT. \href{https://arxiv.org/abs/2203.02155}{https://arxiv.org/abs/2203.02155}
    \item Rafailov, R., Metz, L., Ba, J., et al. (2023). Direct Preference Optimization: Your Language Model is Secretly a Reward Model. \href{https://arxiv.org/abs/2305.18290}{https://arxiv.org/abs/2305.18290}
    \item Dettmers, T., Pagnoini, A., Holtzman, A., et al. (2023). QLoRA: Efficient Finetuning of Quantized LLMs. \href{https://arxiv.org/abs/2305.14314}{https://arxiv.org/abs/2305.14314}
    \item Bai, Y., Kadavath, S., Kundu, S., et al. (2022). Training a Helpful and Harmless Assistant with RLHF. \href{https://arxiv.org/abs/2204.05862}{https://arxiv.org/abs/2204.05862}
    \item Zhang, S., Roller, S., Goyal, N., et al. (2022). OPT: Open Pre-trained Transformer Language Models. \href{https://arxiv.org/abs/2205.01068}{https://arxiv.org/abs/2205.01068}
    \item Hu, E. J., Shen, Y., Wallis, P., et al. (2021). LoRA: Low-Rank Adaptation of Large Language Models. \href{https://arxiv.org/abs/2106.09685}{https://arxiv.org/abs/2106.09685}
    \item Anthropic (2023). Constitutional AI: Harmlessness from AI Feedback. \href{https://www.anthropic.com/}{https://www.anthropic.com/}
    \item HuggingFace. RLHF Course. \href{https://huggingface.co/learn/rlhf-course}{https://huggingface.co/learn/rlhf-course}
  \end{enumerate}
\end{frame}


\begin{frame}{References}
  \footnotesize
  \begin{enumerate}
    \setcounter{enumi}{8}
    \item Stanford CRFM. \textit{CRFM Slides}. \href{http://crfm.stanford.edu/}{http://crfm.stanford.edu/}
  \end{enumerate}
\end{frame}
