% --- Reinforcement Learning for Reasoning Skill Refinement (intro) ---
\section{Reinforcement Learning for Reasoning Skill Refinement}
\begin{frame}[allowframebreaks]{}
    \LARGE Reinforcement Learning for Reasoning Skill Refinement
\framebreak
\end{frame}

\begin{frame}[allowframebreaks]{Reinforcement Learning for Reasoning Skill Refinement}
    \begin{itemize}
        \item \textbf{What is Reinforcement Learning for Reasoning Skill Refinement?}
        \begin{itemize}
            \item A method to enhance reasoning skills in LLMs through reinforcement learning.
            \item Focuses on refining the model's ability to perform reasoning tasks.
        \end{itemize}
        \item \textbf{How does it work?}
        \begin{itemize}
            \item Uses a reward signal to guide the model towards better reasoning performance.
            \item Involves training the model on a variety of reasoning tasks with feedback.
        \end{itemize}
    \end{itemize}
    
    \framebreak
    \begin{itemize}
        \item \textbf{Why is it important?}
        \begin{itemize}
            \item Enhances the model's reasoning capabilities, making it more effective for complex tasks.
            \item Addresses the limitations of traditional training methods by focusing on skill refinement.
        \end{itemize}
        \item \textbf{Challenges}
        \begin{itemize}
            \item Requires a well-defined reward signal to effectively guide the learning process.
            \item Balancing exploration and exploitation during training can be difficult.
        \end{itemize}
    \end{itemize}
\end{frame}
